Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-08-22 prob.tex
prob.tex Fix some typos, but still cannot make a story...

$\bar{\mu}$ cannot correspond to any quantum probability measure.
Suppose $\mu(P)\in\bar{\mu}(P)$ for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$ so that
we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability measure~$\mu$.\qed\end{example}

@@

Discrete interval-valued Gleason's theorem should be here, but we
don't know whether it works or not... Might need to put some extra-conditions
(like \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $}
is too small...) to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.

@@

Might be hard, because let $\mu\otimes\mu$ is not a quantum real-valued
probability measure, where $\mu$ is a non-Born real-valued probability
measure for dimension 2.

>>>>

$\bar{\mu}$ cannot correspond to any quantum probability measure.
Suppose $\mu(P)\in\bar{\mu}(P)$ for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\tensor*[_{\mathscr{O}}]{\sum}{_{j=1}^{N}}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\tensor*[_{\mathbb{R}}]{\sum}{_{j=1}^{N}}q_{j}=1$ and $q_{j}>0$.
However, no pure state~$\ket{\phi}$ satisfies $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$
so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
measure~$\mu$.\qed\end{example}

@@

Discrete interval-valued Gleason's theorem should be here, but we
don't know whether it works or not... Might need to put some extra-conditions
to by-pass the counterexample corresponding to example~\ref{ex:three-dimensional-three-value}.

Following are possible extra-conditions:
\begin{enumerate}
\item \emph{$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $} is
too small...
\item $\mu\otimes\mu$ is not a quantum real-valued probability measure,
where $\mu$ is a non-Born real-valued probability measure for dimension
2. Maybe embedding the small space into the bigger one could add extra-conditions
to kill strange interval-valued probability measures?
\end{enumerate}

@@

Might be hard, because $\mu\otimes\mu$ is not a quantum real-valued
probability measure, where $\mu$ is a non-Born real-valued probability
measure for dimension 2.
